Graphs for 1000  Generations

### 2021-08-04 graphs_newt_snakes/fig_1000.Rmd
I reran the correctted slim script (12 starting points) and the numbers look wild. I also mare the line in params dots and they lined up perfectly.
I updated the r markdown files for the 1000 gen experiments and the finding the correct params to help explain what I am doing and suggest some of the next steps to take.

## The testing Paramiters 
I used different values for snake_mu_effect_sd	newt_mu_effect_sd	snake_mu_rate	newt_mu_rate. I chose these parameters to see if there would be a seeable interaction in phenotypes 
Other params:
	sigma_i = 1, recomb=1e-8, sigma_in = 0.5, sigma_M = 0.33, SD=SI=surs=SM=sigma_in, L = 4, W=35.0, G=1e8, FECUN = 1/(L), RHO, FECUN/((1+FECUN) * K), interaction_rate =  0.05, PE = 0.1, w= 10, c = 0.0, initializeRecombinationRate(recomb), initializeMutationRate(1e-10), initializeGenomicElement(g1, 0, G-1)

@@

Snake/newt mu effect sd -> is the standard deviation that each mutation would "effect" a phenotype. Values: 0.01 0.05 0.2 0.5

Snake/newt mu rate -> is the mutation rate that were assigned to newts and snakes. Values: 1.00E-08 1.00E-10 1.00E-12

@@

-Realistic phenotypes (snake 0-3, newt 0-1.5(thoughts 2021?))
-See if the levels of toxicity and resistance interact 
-See groups of mutations/ certain phenotypes

@@

  file1 <- read.table(files[1], header = TRUE)
  file1$Newt_mean_Pheno[file1$Newt_mean_Pheno == "NULL"] <- NA
  file1$Snake_mean_Pheno[file1$Snake_mean_Pheno == "NULL"] <- NA
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_1)+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle(title) +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
  file <- file[complete.cases(file), ]
 p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color = darken("darkred")) +
   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color = darken("steelblue")) +
  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color = lighten("steelblue"))+
  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1), size = 0.3, arrow = arrow(length = unit(0.5, "cm")), color="darkred")+
   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1), size = 0.3, arrow = arrow(length = unit(0.5, "cm")), color="steelblue")

 i = i+1
}
return(p)
}

@@

Loop through the files and find the max and min of each of the species phenotypes
Then set up a graph with the average phenotype:

@@

@@

I ran 144 SLiM simulations with different parameters values and used the MSprime   both_su_1e-10_nu_1e-10_sue_0.01_nue_0.01 (s/n u mutation rate, n/s ue mutation effect size) file.

@@

@@

Extra note: In my code snake_mu_rate is called mu_rate

@@

@@

>>>>

## Fake Example of the Problem I have been seeing

```{r fake exaple, echo=FALSE}
gen <- seq(20, 1000, by = 20)
  ex <- as.data.frame(gen)

ex$Newt_mean_Pheno <- pexp(seq(0.2, 10, by = .2), rate = 1)*seq(1, 100, by = 2) + rnorm(50, mean = 0, sd = 5)
  ex$Snake_mean_Pheno <-seq(.18, 5.1, by = .1) + + rnorm(50, mean = 0, sd = 5)
p <- ggplot(ex, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_1)+
  geom_line(aes(y = Newt_mean_Pheno, colour="Newt")) + 
  geom_line(aes(y = Snake_mean_Pheno, colour="Snake"), linetype="twodash")+
  ggtitle("Fake Example of What I was Observing") +
  xlab("Generation") + ylab("Average Phenotypes")+
  scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
  theme_bw()
p
```

## The testing Paramiters 
I used different values for snake_mu_effect_sd	newt_mu_effect_sd	snake_mu_rate	newt_mu_rate. I chose these parameters to see if there would be a see-able interaction in phenotypes 
Other params:
	sigma_i = 1, recomb=1e-8, sigma_in = 0.5, sigma_M = 0.33, SD=SI=surs=SM=sigma_in, L = 4, W=35.0, G=1e8, FECUN = 1/(L), RHO, FECUN/((1+FECUN) * K), interaction_rate =  0.05, PE = 0.1, w= 10, c = 0.0, initializeRecombinationRate(recomb), initializeMutationRate(1e-10), initializeGenomicElement(g1, 0, G-1)

@@

**Snake/newt mu effect sd -> is the standard deviation that each mutation would "effect" a phenotype. Values: 0.01 0.05 0.2 0.5**

**Snake/newt mu rate -> is the mutation rate that were assigned to newts and snakes. Values: 1.00E-08 1.00E-10 1.00E-12**

@@

* Realistic phenotypes (snake 0-3, newt 0-1.5(thoughts 2021?))
* See if the levels of toxicity and resistance interact 
* See groups of mutations/ certain phenotypes

@@

  file1 <- read.table(files[1], header = TRUE)
  file1$Newt_mean_Pheno[file1$Newt_mean_Pheno == "NULL"] <- NA
  file1$Snake_mean_Pheno[file1$Snake_mean_Pheno == "NULL"] <- NA
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_1)+
  geom_line(aes(y = Newt_mean_Pheno, colour="Newt")) + 
  geom_line(aes(y = Snake_mean_Pheno, colour="Snake"), linetype="twodash")+
  ggtitle(title) +
  xlab("Generation") + ylab("Average Phenotypes")+
  scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
  theme_bw()

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
  file <- file[complete.cases(file), ]
 p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color= darken("darkred")) +
   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color=lighten("darkred"))  + 
  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color=darken("steelblue")) +
  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color=lighten("steelblue"))+
  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1, colour="Newt"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))+
   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1, colour="Snake"), size = 0.3, arrow = arrow(length = unit(0.5, "cm")))

 i = i+1
}
p <- p +
 scale_colour_manual(name = "Species", values = c("Newt" = "darkred", "Snake"="steelblue"))
return(p)
}

@@

Loop through the files and find the max and min of each of the species phenotypes
Then set up a graph with the average phenotype per generation:
I collected data ever 20 generations until 1000 generations were done

@@

Here I have a questions why are the newts always starting off higher than the snakes????

@@

I ran 144 SLiM simulations(might be 143?) with different parameters values and used the MSprime file: both_su_1e-10_nu_1e-10_sue_0.01_nue_0.01 (s/n u mutation rate, n/s ue mutation effect size)

@@

```
I noticed that in a majority of these the newts had a higher phenotype than the snakes.

@@

Extra note: In my code snake_mu_rate is called mu_rate
**I found an error in the code which was not giving the correct mutation rate to snakes**

@@

Some of these values seem very large, but the means are not super bad.

@@

## Next Steps

Some of these simulations still created very large phenotypes. I would like to know why
*Was it the mutation or effect size values?
*Is it the msprime simulation starting point?
*Is the maximum value important? And if so what does it mean?
*Compare simulated phenotype values to the predicted values from the equation mediated by the parameters
*Is this caused by space?
*Is it caused by co-evolution?
